---
title: "Article 2"
description: |
  A new article created using the Distill format.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web. 

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.

Adding some text to test out the footnotes option ^[putting text in here] and it says that they auto number footnotes ^[this should be number two] if that is true.


An aside is when you put info to far right of doc called the gutter. This should start an aside:

<aside>this is a text aside </aside>

They can also be code chunks such as plots:

<aside>
```{r}
plot(cars)
```
</aside>

see if that worked

## Acknolwedgements {.appendix}

this is content for the appendix



